Preliminary Thesis Defence

### 2014-01-06 south-africa.tex
finish SA

\subsubsection{Height-Based Z-scores}
\label{sa:se:hbz}
The Height-Based Z-scores (HBZs) are the Weight-for-Height Z-score (WHZ)
and Body Mass Index Z-score (BMIZ).
Where the BMI (or Quetelet) is a transformed version of the WHZ, which has a quadratic height effect.
The equation for BMI is:
\[
\textbf{BMI} = \frac{\textbf{weight(kg)}}{\textbf{height(m)}^2}
\]

@@

\section{Results}
\label{sa:results}
In \autoref{sa:hazwaz} we present our estimation results for the age-based z-scores,
and in \autoref{sa:whzbmiz} we present our estimation results for the height-based z-scores.

@@

% LaTeX table created manually
% Fri Dec 27 23:22:00 2013
\begin{table}[!ht]
\centering
\caption{Age-Based Z-scores}
\label{sa:hazwaz}
\begin{tabular}{l|rrr|rrr}
% \hline
& \multicolumn{3}{c}{Height for Age Z-score} & \multicolumn{3}{c}{Weight for Age Z-score}\\
\hline
specification & 1 & 2 & 3 & 1 & 2 & 3\\
\hline
w\_spen\_m & 0.2366 & *0.8228 & 0.7908 & 0.2366 & 0.2981 & 0.4780 \\
w\_spen\_w & -0.2331 & 0.1053 & 0.1072 & -0.2331 & -0.3112 & -0.3280 \\
elig.men.60 & & **-0.3419 & **-0.3465 & & ***-0.3475 & **-0.3243 \\
w\_spen\_m1:elig.men.60 & & & 0.0446 & & & -0.2545 \\
% \hline
w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 & -0.0000 & -0.0000 & -0.0000 \\
\end{tabular}
\end{table}

As \autoref{sa:hazwaz} shows both the Height-for-Age and the Weight-for-Age estimations for all three Right-Hand Side variations give similar results.
For all the height-based z-score estmations, we find that the policy variable \textbf{elig.men.60} has a negative coefficient estimate, which is highly significant (where included).
In all cases the estimate has a p-value of less that \textbf{0.01}.
Meaning that (meta-discussion aside) the probabiliy that this coefficient represents a non-existant relation (Type II error) is less than one percent.
In the model 2 specification of the Weight-for-Height dependent variable, the p-value is even less that 0.001.
However, upon the inclusion of the interaction term (model 3) this falls back to below 0.01.

@@

Furthermore, when using Height-for-Age as the LHS, and the model 2 on the HRS, we find a positive effect of living with a male pension recipient.
The coefficient output here is no longer significant when we include the interaction term in the model 3 specification.

@@

% LaTeX table created manually
% Fri Dec 27 23:53 2013
\begin{table}[!ht]
\centering
\caption{Height-Based Z-scores}
\label{sa:whzbmiz}
\begin{tabular}{l|rrr|rrr}
& \multicolumn{3}{c}{Weight for Height Z-score} & \multicolumn{3}{c}{Body Mass Index Z-score}\\
\hline
specification & 1 & 2 & 3 & 1 & 2 & 3 \\
\hline
w\_spen\_m &  -0.3532 & -0.3210 & -0.4303 & *-0.8058 & *-0.7905 & *-1.0226 \\
w\_spen\_w & 0.0655 & 0.0371 & 0.0478 & -0.1592 & -0.1956 & -0.1742 \\
elig.men.60 & & -0.1417 & -0.1574 & & -0.1674 & -0.2049 \\
w\_spen\_m1:elig.men.60 & & & 0.1484 & & & 0.3407 \\
w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 & -0.0000 & 0.0000 & 0.0000
\end{tabular}
\end{table}

In \autoref{sa:whzbmiz} we do not find an effect of the \textbf{elig.men.60} variable.
In the WHZ estimation we do not find any significant variables.
However, the \textbf{BMIZ} estimation we find \textbf{w\_spen\_m} to be significant at a 5\% level of all specifications.

@@

For the higher coefficient estimates, it is important to note that \textbf{BMIZ} is essentially a convex mapping of \textbf{WHZ},
since height is squared in the denominator of the BMI function, as described in \autoref{sa:se:hbz}.
In other words, the fact that the estimators, which give transformed coefficient estimates can have different significance levels,
can be explained as follows.
The squaring of the height in the denominator of the Body-Mass Index function, makes it a non-linear mapping of the Weight-for-Height Z-scores.
Furthermore, from the significance at the 5\% level of the coefficients in the \textbf{BMIZ} estimations,
we can conclude that the coefficient estimates are higher that the standard error estimates,
by a factor of several times (for Degrees of Freedom $\sim 380$).
Combining the small estimates of the standard errors, with the convex mapping,
gives the results that the standard errors are scaled up to a lesser degree than the coefficient estimates.
This then gives the results, that with t-testing the significance of the convexly mapped coefficients and standard errors,
we can find significance at the 5\% level for the convexly mapped \textbf{BMIZ} estimates of \textbf{w\_spen\_m},
where for the \textbf{WHZ} estimates of \textbf{w\_spen\_m} we could not.

@@

% RECOMMENDATIONS
% estimate using by weighting the drop for women with life exp. evolution, and male also
% or use the drop for women (unaffected) to scale men and women back to 2008 levels.

>>>>

\subsubsection{Height-Based Z-scores}
\label{sa:hbz}
The Height-Based Z-scores (HBZs) are the Weight-for-Height Z-score (WHZ)
and Body Mass Index Z-score (BMIZ).
Where the BMI (or Quetelet) is a transformed version of the WHZ, which has a quadratic height effect.
The equation for BMI is:
\[
\textbf{BMI} = \frac{\textbf{weight(kg)}}{\textbf{height(m)}^2}
\]

@@

\section{Results}
\label{sa:results}
In \autoref{sa:ta:haz} and \autoref{sa:ta:waz} we present our estimation results for the age-based z-scores.
In \autoref{sa:ta:whz} and \autoref{sa:ta:bmiz} we present our estimation results for the height-based z-scores.

@@

% LaTeX table created manually
% Fri Dec 27 23:22:00 2013
\begin{table}[!ht]
\centering
\caption{Height-for-Age Z-score}
\label{sa:ta:haz}
\begin{tabular}{l|rrr}
\hline
specification & 1 & 2 & 3\\
\hline
w\_spen\_m & 0.2366 & *0.8228 & 0.7908 \\
w\_spen\_w & -0.2331 & 0.1053 & 0.1072 \\
elig.men.60 & & **-0.3419 & **-0.3465 \\
w\_spen\_m1:elig.men.60 & & & 0.0446 \\
w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
\end{tabular}
\end{table}

% LaTeX table created manually
% Fri Dec 27 23:22:00 2013
\begin{table}[!ht]
\centering
\caption{Weight-for-Age Z-score}
\label{sa:ta:waz}
\begin{tabular}{l|rrr}
\hline
specification & 1 & 2 & 3\\
\hline
w\_spen\_m & 0.2366 & 0.2981 & 0.4780 \\
w\_spen\_w & -0.2331 & -0.3112 & -0.3280 \\
elig.men.60 & & ***-0.3475 & **-0.3243 \\
w\_spen\_m1:elig.men.60 & & & -0.2545 \\
w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
\end{tabular}
\end{table}

As \autoref{sa:ta:haz} and \autoref{sa:ta:waz} shows the Height-for-Age and the Weight-for-Age estimations for all three Right-Hand Side variations give similar results.
For all the height-based z-score estmations, we find that the policy variable \textbf{elig.men.60} has a negative coefficient estimate, which is highly significant (where included).
In all cases the estimate has a p-value of less that \textbf{0.01}.
Meaning that (meta-discussion aside) the probabiliy that this coefficient represents a non-existant relation (Type II error) is less than one percent.
In the model 2 specification of the Weight-for-Height dependent variable, the p-value is even less that 0.001.
However, upon the inclusion of the interaction term (model 3) this falls back to below 0.01.

@@

Furthermore, when using Height-for-Age as the LHS, and the model 2 on the RHS,
we find a positive effect of living with a male pension recipient.
However, the coefficient output here is no longer significant when we include the interaction term in the model 3 specification.

@@

% LaTeX table created manually
% Fri Dec 27 23:53 2013
\begin{table}[!ht]
\centering
\caption{Weight-for-Height Z-score}
\label{sa:ta:whz}
\begin{tabular}{l|rrr}
\hline
specification & 1 & 2 & 3 \\
\hline
w\_spen\_m &  -0.3532 & -0.3210 & -0.4303 \\
w\_spen\_w & 0.0655 & 0.0371 & 0.0478 \\
elig.men.60 & & -0.1417 & -0.1574 \\
w\_spen\_m1:elig.men.60 & & & 0.1484 \\
w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
\end{tabular}
\end{table}

% LaTeX table created manually
% Fri Dec 27 23:53 2013
\begin{table}[!ht]
\centering
\caption{Body-Mass-Index Z-score}
\label{sa:ta:bmiz}
\begin{tabular}{l|rrr}
\hline
specification & 1 & 2 & 3 \\
\hline
w\_spen\_m & *-0.8058 & *-0.7905 & *-1.0226 \\
w\_spen\_w & -0.1592 & -0.1956 & -0.1742 \\
elig.men.60 & & -0.1674 & -0.2049 \\
w\_spen\_m1:elig.men.60 & & & 0.3407 \\
w\_h\_tinc & -0.0000 & 0.0000 & 0.0000\\
\end{tabular}
\end{table}

In \autoref{sa:ta:whz} and \autoref{sa:ta:bmiz} we do not find an effect of the \textbf{elig.men.60} variable.
In the WHZ estimation we do not find any significant variables.
However, the \textbf{BMIZ} estimation we find \textbf{w\_spen\_m} to be significant at a 5\% level of all specifications.

@@

For the higher coefficient estimates, it is important to note that \textbf{BMIZ} is essentially a convex mapping of \textbf{WHZ},
since height is squared in the denominator of the BMI function, as described in \autoref{sa:hbz}.
In other words, the fact that the estimators, which give transformed coefficient estimates can have different significance levels,
can be explained as follows.
The squaring of the height in the denominator of the Body-Mass Index function, makes it a non-linear mapping of the Weight-for-Height Z-scores.
Furthermore, from the significance at the 5\% level of the coefficients in the \textbf{BMIZ} estimations,
we can conclude that the coefficient estimates are higher that the standard error estimates,
by a factor of several times (for Degrees of Freedom $\sim 380$).
Combining the small estimates of the standard errors, with the convex mapping,
gives the results that the standard errors are scaled up to a lesser degree than the coefficient estimates.
This then gives the results, that with t-testing the significance of the convexly mapped coefficients and standard errors,
we can find significance at the 5\% level for the convexly mapped \textbf{BMIZ} estimates of \textbf{w\_spen\_m},
where for the \textbf{WHZ} estimates of \textbf{w\_spen\_m} we could not.

@@
